Whittaker Models for Real Groups

### 2024-04-15 whittaker.tex
More tinkering

Suppose $\pi$ is an irreducible representation of~$G(\R)$. Recall $\pi$ has a \emph{Whittaker model} when there exists a pair $(B(\R), \chi)$ where 
\begin{enumerate}[(i)]
\item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$;
\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space;
\end{enumerate}
such that~$\pi$ embeds into the induced representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$. Of course this can happen if and only if there exists a Borel subgroup $B \subset G$ satisfying~(i); by definition this means~$G$ is \emph{quasisplit}, which we assume from now on.

@@

Now suppose~$\pi$ is a generic discrete series representation of~$G(\R)$. Then the Whittaker datum $\mathfrak{w}(\pi)$, the wavefront set $\WF(\pi)$ and the associated variety $\AV(\pi)$ basically contain the same information: given one of the three invariants, it is possible to reconstruct the other two. This is well known to the experts, but not so easy to extract from the literature, especially not if one wants to be explicit about how to pass back and forth between the three invariants. We have felt it worthwhile to give an account of the matter here.

@@

\footnote{AA 02-IV-2024: should of course rewrite this section once the rest is stable.}

@@

Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph. }
. In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint. Nevertheless $H_{\lambda}$ and $H_\theta=[E_\theta, F_\theta]$ are in the same Weyl chamber. Therefore the result follows from:

@@

>>>>

Suppose $\pi$ is an irreducible representation of~$G(\R)$. Recall $\pi$ has a \emph{Whittaker model} when there exists a pair $(B(\R), \chi)$ where 
\begin{enumerate}[(i)]
\item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$,
\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space,
\end{enumerate}
such that~$\pi$ embeds into the induced representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$. Of course this can happen if and only if there exists a Borel subgroup $B \subset G$ satisfying~(i); by definition this condition means~$G$ is \emph{quasisplit}, which we assume from now on.

@@

Now suppose~$\pi$ is a generic discrete series representation of~$G(\R)$. Then the Whittaker datum $\mathfrak{w}(\pi)$, the wavefront set $\WF(\pi)$ and the associated variety $\AV(\pi)$ basically contain the same information: given one of the three invariants, it is possible to reconstruct the other two. This is well known to the experts, but some aspects of this discussion are not  easy to extract from the literature, especially not if one wants to be explicit about how to pass back and forth between the three invariants. We have felt it worthwhile to give an account of the matter here.

@@

\footnote{AA 02-IV-2024: I didn't make any effort at polishing this in recent weeks; we should of course rewrite this section once the rest is stable.}

@@

Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph. }.
In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint. 
Nevertheless $H_{\lambda}$ and $H_\theta=[E_\theta, F_\theta]$ are in the same Weyl chamber\footnote{AA 2024-IV-15: should probably explain a bit more why this is correct.}.
Therefore the result follows from:

@@

The connection between Lemma~\ref{lem:Kost_and_AC} and Proposition~\ref{prop:AC_chamber} is that Lemma~\ref{lem:Kost_and_AC}  implies the  following observation on the behavior of the asymptotic cone of regular semisimple orbits:
